Proposed Solution

### 2016-11-11 Ennan-Proposal/motivation.tex
stuff

Building such an automatic verification framework for
configuration files requires addressing several challenges. 
First, in the process of inferring a specification, we have to 
analyze mainly with an untyped, unstructured sequence of assignments.
Thus, we need to develop a suitable language model. We do that by 
``guessing'' a type of variables and then deriving formulas that
describe relationships between these variables. However, the
type of a variable cannot always be fully determined 
from a single value. 
An entry {\tt general\_log = 1} assigns an integer to the 
variable {\tt general\_log}. However, 1 here is a Boolean variable,
which denotes that there will be a general log file.
Another example, which shows how this can easily lead to an error, is 
that sometimes a configuration files 
contain the following entry {\tt general\_log = /var/log/mysql/mysql.log}. This will cause    
\ruzica{what will actually happen in this case}
Some existing type inference 
work would report this is an error, because {\tt temp\_dir} should be assigned
an integer~\cite{zhang14encore}. We address this problem by introducing the concept of
{\emph{probabilistic types}}.
Rather than assigning only one variable to a single type, 
we assign several types over a probability distribution. 
Using probabilistic types,
we aim to generate a more accurate language model,
thus significantly improving our verification capabilities.

Second, we will learn patterns describing variables and their relations. We will associate with each type a set of very general templates. The user does not need to provide any templates -- they are internally associated to the types.
Nevertheless, in addition to those general templates, we still need specific algorithms to learn
rules that cannot be easily templated.

From a practical perspective, we do not want to introduces any additional burden 
to the user: they can simply use \app to check for errors in their
configuration files. However, they can also easily extend the framework
themselves. The system is designed to be highly modular. If there is a
class of rules that \app is not currently learning, the user can develop
her own templates and learners for that class. The new learner can be
added to \app and this way it can check an additional new set of
errors.

Our \app prototype still has many limitations:
for example, we cannot handle configuration errors that can be 
triggered during system execution time.
Nevertheless, we believe \app may suggest a practical path
toward automatic and modular language-based configuration verification.
To summarize, this tool paper makes the following contributions:

\begin{enumerate}

\item We propose the first automatic configuration verification
framework, \app, that can learn a language model from a sample
dataset, and then use this language model to verify 
configuration files of interest.

\item \app proposes probabilistic types to assign a confidence 
distribution over a set of types to each entry, 
while generating the intermediate representation.

\item \app employs a collection of machine learning algorithms to 
enable powerful rule and constraint inference.

\item \app is capable of detecting various tricky errors that cannot
be detected by previous efforts,
including entry ordering errors, fine-grained value correlation errors, 
missing entry errors, and environment-related errors.

\item We implement a \app prototype and evaluate it by
conducting comprehensive experiments on real-world dataset.

\end{enumerate}

>>>>

Building such an automatic verification framework for
configuration files requires addressing several challenges. 
First, in the process of inferring a specification, we have to 
analyze mainly with an untyped, unstructured sequence of assignments.
Thus, we need to develop a suitable language model. We do that by 
``guessing'' a type of variables and then deriving formulas that
describe relationships between these variables. However, the
type of a variable cannot always be fully determined 
from a single value. 
An entry {\tt general\_log = 1} in a MySQL configuration file assigns an integer to the 
variable {\tt general\_log}. However, 1 here is a Boolean variable,
which denotes that there will be a general log file.
Another example, which often appears in practice, shows how variable names and 
their ``types'' can easily lead to an error. Consider the
following entry {\tt general\_log = /var/log/mysql/mysql.log}. Although this statement 
alone might look correct, this is actually a typing error and as a result MySQL log cannot be correctly written.

Second, we will learn patterns describing variables and their relations. We will associate with each type a set of very general templates. The user does not need to provide any templates -- they are internally associated to the types.
Nevertheless, in addition to those general templates, we still need specific algorithms to learn
rules that cannot be easily templated (such as ordering rules).

We will implement this verification framework and call it \app (for continuity reasons
-- our preliminary tool was called ConfigC, cf. next section).

### 2016-11-11 Ennan-Proposal/prelim.tex
stuff

We have proposed and developed a preliminary system, named
ConfigC~\cite{santolucitoCAV}, which is (to the best of
our knowledge) the first systematic effort capable of automatically
verifying configuration files before the configuration files
are deployed and installed.
In particular, ConfigC is a framework that first automatically
analyzes datasets of correct configuration files, 
and then derives rules for building a language model 
from the give datasets.
Finally, the resulting language model could be used to verify 
new configuration files (called target configuration files) and 
detect errors in these target configuration files.
The configuration errors ConfigC can deal with cover:
entry missing errors, ordering errors, type errors and
value correlation.
To our knowledge, there is no existing effort that is able to detect
the above errors, because they are very tricky to identify in
practice.

>>>>

Based on our own experience with misconfigurations,
we have proposed and developed a simple tool for verification of 
configuration files, named
ConfigC~\cite{santolucitoCAV}. Motivated by promising preliminary
results, which we obtained with ConfigC, we believe that automated 
verification of configuration files, before they
are deployed and installed, is possible and that it should be further studied.

From ConfigC we drew the main inspiration for this proposal. In particular, 
ConfigC is a framework that first automatically
analyzes datasets of correct configuration files, 
and then derives rules for building a language model 
from the given datasets.
Finally, the resulting language model could be used to verify 
new configuration files (called target configuration files) and 
detect errors in these target configuration files.
The configuration errors ConfigC can deal with cover:
entry missing errors, ordering errors, type errors and
value correlation.
To our knowledge, there is no existing effort that is able to detect
the above errors, because they are very tricky to identify in
practice.
